Kindly Bent to Free Us

### 2019-11-12 kindly/lang.tex
Fixed uses of 'note' instead of 'denote' and various typos.
Added syntactic category for multiplicities, simplified lattice rules, fixed syntax-directed kinding rules to match syntax (applied type constructors instead of type constructors).

A type $\tau$ is either a type variable, a function type indexed by a
kind,
a type application $\tapp{t}{\Multi{\tau}}$ of an abstract type constructor
$\T t$, or a borrowed type  $\borrowty{k}{\tau}$.

@@

% Let us first define our conventions and meta-syntactic variables.
% Expressions, types and kinds are noted respectively $e$, $\tau$, and $k$.
% Variables, type variables and kind variables are noted
% respectively $x$, $\tvar$ and $\kvar$. Types and kind schemes
% are noted $\schm$ and $\kschm$.
% In the rest of the text, we will write lists with a bar and an index, for
% instance $\Multi[i]{\tau}$.
% Kind constants are noted in bold capital letters, such as $\kaff$ for affine.

% The syntax of \lang is presented in \cref{grammar} and follows
% traditional ML languages with let bindings.
% Borrows, noted $\borrow{e}$, are annotated with a specification indicating
% if a borrow is immutable ($\IBORROW$) or mutable ($\MBORROW$).
% We also distinguish reborrows, which are noted $\reborrow{e}$.
% Match are indexed with a specification which can be either $\&^b$
% (which $b$ a borrow specification) or $id$, indicating if the match
% should operate on borrows or not.
% Regions, noted $\region{\Sone x\BORROW}{e}$ are annotated with their nesting ($n$)
% and the variable whose borrow they enclose ($x$).
% %
% $\tapp{t}{\Multi{\tau}}$ denotes a type application where
% $\T t$ is an abstract type constructor.
% Arrow and borrow types are annotated with a kind, noted $\tau \tarr{k} \tau$
% and $\borrowty{k}{\tau}$ respectively.
% %
% Kinds can be either a kind variable $\kvar$, or constants
% (linear $\klin$, affine $\kaff$ or unrestricted $\kun$) indexed
% by a nesting level represented by a member of $N \cup \{\infty\}$.
% Type schemes and kind schemes are guarded by a set of constraints.
% %
% Finally, constraints are composed of a list of kind inequalities.

@@

% , either
% through
% linearity and affinity which restrict how variables are shared and ignored,
% or through borrows which allow to circumvent the linearity rules
% in a controlled way.
% In order to check these properties, we introduce several new bindings
% in our typing environments.
% The grammar of type environment (noted $\E$) is shown in \cref{grammar:env}.

>>>>

A type $\tau$ is either a type variable, a function type indexed by a
kind,
a type application $\tapp{\tcon}{\Multi{\tau}}$ of an abstract type constructor
$\T t$, or a borrowed type  $\borrowty{k}{\tau}$.

@@

% Let us first define our conventions and meta-syntactic variables.
% Expressions, types and kinds are denoted respectively as $e$, $\tau$, and $k$.
% Variables, type variables and kind variables are denoted
% respectively as $x$, $\tvar$ and $\kvar$. Types and kind schemes
% are denoted by $\schm$ and $\kschm$.
% In the rest of the text, we will write lists with a bar and an index, for
% instance $\Multi[i]{\tau}$.
% Kind constants are denoted in bold capital letters, such as $\kaff$ for affine.

% The syntax of \lang is presented in \cref{grammar} and follows
% traditional ML languages with let bindings.
% Borrows $\borrow{e}$ are annotated with a specification indicating
% if a borrow is immutable ($\IBORROW$) or mutable ($\MBORROW$).
% We also distinguish reborrows, which are written as $\reborrow{e}$.
% Match are indexed with a specification which can be either $\&^b$
% (which $b$ a borrow specification) or $id$, indicating if the match
% should operate on borrows or not.
% Regions $\region{\Sone x\BORROW}{e}$ are annotated with their nesting ($n$)
% and the variable whose borrow they enclose ($x$).
% %
% $\tapp{\tcon}{\Multi{\tau}}$ denotes a type application where
% $\T t$ is an abstract type constructor.
% Arrow and borrow types are annotated with a kind, written as $\tau \tarr{k} \tau$
% and $\borrowty{k}{\tau}$ respectively.
% %
% Kinds can be either a kind variable $\kvar$, or constants
% (linear $\klin$, affine $\kaff$ or unrestricted $\kun$) indexed
% by a nesting level represented by a member of $N \cup \{\infty\}$.
% Type schemes and kind schemes are guarded by a set of constraints.
% %
% Finally, constraints are composed of a list of kind inequalities.

@@

% , either
% through
% linearity and affinity which restrict how variables are shared and ignored,
% or through borrows which allow to circumvent the linearity rules
% in a controlled way.
% In order to check these properties, we introduce several new bindings
% in our typing environments.
% The grammar of type environment (denoted $\E$) is shown in \cref{grammar:env}.

### 2019-11-12 kindly/sdtyping/extra.tex
Add kinding rules for pairs.
Added syntactic category for multiplicities, simplified lattice rules, fixed syntax-directed kinding rules to match syntax (applied type constructors instead of type constructors).

We write $\inferSK{C}{\E}{\tau}{k}$
if $\tau$ has kind $k$ in environment $\E$ under constraints $C$.
The rules are shown in \cref{rules:sd-kinding}.
Kinds and types follow a small calculus with variables ($\tvar$,\dots),
functions (type constructors $\T{t}$), application ($\tapp{t}{\Multi{\tau}}$)
and primitives such as types for arrows ($\tau\tarr{k}\tau'$) and
borrows ($\borrowty{k}{\tau}$).
Kind checking can thus be done in a fairly straightforward, syntax-directed
fashion by simply following
the syntax of the types. Kind arrows can only appear when looking
up the kind scheme of a type constructor $\T t$. Kind arrows are forbidden
in any other contexts.

>>>>

We write $\inferSK{C}{\E}{\tau}{k}$
if $\tau$ has kind $k$ in environment $\E$ under constraints $C$.
The rules are shown in \cref{rules:sd-kinding}.
Kinds and types follow a small calculus with variables ($\tvar$,\dots),
functions (type constructors $\T{t}$), application ($\tapp{\tcon}{\Multi{\tau}}$)
and primitives such as types for arrows ($\tau\tarr{k}\tau'$) and
borrows ($\borrowty{k}{\tau}$).
Kind checking can thus be done in a fairly straightforward, syntax-directed
fashion by simply following
the syntax of the types. Kind arrows can only appear when looking
up the kind scheme of a type constructor $\T t$. Kind arrows are forbidden
in any other contexts.
